%-------------------------
% ATS-Optimized Resume - 1 Page
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{fontawesome5}

\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule \vspace{-5pt}]

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} $|$ \emph{\small#2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge Jayesh Kumavat} \\
  \vspace{3pt}
  \small \hspace{1pt} \href{tel:+918928910306}{\faPhone\ +91-8928910306} $|$ \hspace{1pt} \href{mailto:jayeshkumavat42@gmail.com}{\faEnvelope\ jayeshkumavat42@gmail.com} $|$
  \hspace{1pt} \href{https://github.com/jayesh-kumavat}{\faGithub\ Github} $|$ \hspace{1pt} \href{https://www.linkedin.com/in/jayesh-kumavat-03709630a/}{\faLinkedin\ Linkedin} $|$ \hspace{1pt} \faMapMarker* \texttt{Pune, Maharashtra}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\begin{itemize}[leftmargin=0in, label={}]
  \item\small{
    Software Engineer with 2+ years of experience in backend development, REST API design, and scalable system architecture. Skilled in Node.js, Express, Python, MongoDB, PostgreSQL, and cloud services (AWS, Cloudinary) to build production-grade web applications. Experience in authentication systems, payment integration, real-time features, and agile delivery. Proven ability to design robust APIs, implement secure auth flows, and deliver end-to-end backend solutions for cross-functional teams.
  }
\end{itemize}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0in, label={}]
  \small{\item{
    \textbf{Languages:} JavaScript, TypeScript, Python, SQL, Java, C++ \\
    \textbf{Backend:} Node.js, Express.js, REST APIs, JWT Authentication, Middleware, WebSockets \\
    \textbf{Databases:} MongoDB, PostgreSQL, MySQL, Redis, Mongoose ODM \\
    \textbf{Frontend:} React, Redux Toolkit, Tailwind CSS, HTML/CSS \\
    \textbf{Tools:} Docker, Git, GitHub Actions, Postman, Jira, Confluence \\
    \textbf{Cloud \& Services:} AWS (S3, Lambda, CloudWatch), Cloudinary, Razorpay, Nodemailer \\
    \textbf{Methodologies:} Agile, Scrum, CI/CD, Test-Driven Development, Microservices
  }}
\end{itemize}

%-----------PROFESSIONAL EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Programmer Analyst}{Aug 2024 -- Present}
      {Cognizant -- Charter Communications (Data Exchange Team)}{Pune, India}
      \resumeItemListStart
        \resumeItem{Developed and maintained ETL pipelines using Python, SQL, and Shell Script to deliver datasets to 5+ internal business teams.}
        \resumeItem{Processed 100+ GB datasets using memory-efficient batch processing, reducing CPU and memory usage by 40\%.}
        \resumeItem{Built and scheduled Apache Airflow DAGs and NiFi flows for automated orchestration, reducing manual intervention by 60\%.}
        \resumeItem{Implemented monitoring, retry logic, and alerting mechanisms to achieve 99\% pipeline uptime.}
        \resumeItem{Wrote SQL queries for data extraction, transformation, and validation against PostgreSQL and Oracle databases.}
        \resumeItem{Collaborated with cross-functional teams in agile sprints to gather requirements and deliver production-ready solutions.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Engineering Intern}{Dec 2023 -- May 2024}
      {Cognizant Technology Solutions}{Coimbatore, India}
      \resumeItemListStart
        \resumeItem{Built data ingestion proof-of-concepts with schema validation and automated scheduling using Airflow and NiFi.}
        \resumeItem{Developed incremental load strategies and streaming utilities to process large files without memory overflow.}
        \resumeItem{Created runbooks and automated test suites for production handover, reducing onboarding time by 50\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\href{https://github.com/jayesh-kumavat/StudyNotion}{StudyNotion -- Ed-Tech Platform}}{Node.js, Express, MongoDB, React, Redux, Cloudinary, Razorpay}
      \resumeItemListStart
        \resumeItem{Architected full-stack ed-tech platform with 12+ RESTful API modules (auth, courses, payments, admin, AI assistant) serving instructors, students, and admins.}
        \resumeItem{Implemented secure JWT authentication with access/refresh token rotation, session management with inactivity-based timeout, and role-based access control.}
        \resumeItem{Integrated Razorpay payment gateway for course purchases with server-side capture and verification, and Cloudinary for video/image/file uploads.}
        \resumeItem{Built AI-powered lecture assistant using Groq SDK (Llama 3.1 + Whisper) with auto-transcription via ffmpeg audio extraction and conversational context management.}
        \resumeItem{Designed gamification system with event-driven point allocation, leaderboard, personalized course recommendations, and discussion forums with nested replies.}
        \resumeItem{Developed admin panel with platform analytics, user/course moderation, category management, and transaction history APIs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {B.Tech in Mechanical Engineering (Minor: Computer Science)}{Aug 2019 -- Jun 2023}
      {Institute of Infrastructure Technology Research and Management}{Ahmedabad, India}
      \resumeItemListStart
        \resumeItem{CGPA: 7.6/10 | Coursework: Data Structures and Algorithms, Design and Analysis of Algorithms, AI and Machine Learning, Computer Networking}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}
